### 2025-01-27 our_article/MCM_article/article_file.tex
updated

@@

        It can be mathematically proven that, after incorporating these variations, 
        the LV-LG model system theoretically possesses non-trivial stable points when the parameters are within a certain range. 
        When the system is near these points, the ecosystem can recover from small perturbations, 
        reaching a dynamic ecological equilibrium.
      \subsubsection{Soil Fertility}
        Now, we introduce the effect of soil fertility on plant growth.
        $i$ in the following statements represents rice or weed, $j$ the other.
        For the sake of simplicity in the model, 
        the influence of soil fertility on plant growth is divided into two main factors: 
        the effect of carbon dioxide (CO$_2$) concentration and the concentration of inorganic salts absorbed by the plants.

@@

    Below, we analyze the curves for each of the four scenarios:
    \begin{itemize}
      \item Effect of \( r_{crp} \) (natural growth rate of rice biomass):** 
      As shown in Figure \ref{fig:Change_all} (A), an increase in \( r_{crp} \) leads to an upward trend in rice biomass at any given time, and vice versa. 
      From an ecological perspective, an increase in \( r_{crp} \) indicates a higher marginal growth rate of rice biomass, resulting in faster growth, 
      which aligns with the figure. On the other hand, 
      the overall evolutionary trend of the system remains approximately the same when \( r_{crp} \) varies within a certain range, 
      reflecting the system's stability.
      \item Effect of \( \beta_{c\rightarrow w} \) (weed-to-rice competition coefficient):** As shown in Figure \ref{fig:Change_all} (B), 
      an increase in \( \beta_{c\rightarrow w} \) results in a downward trend in rice biomass and an upward trend in weed biomass at any given time, 
      and vice versa. Ecologically, an increase in \( \beta_{c\rightarrow w} \) reflects a higher competitive ability of weeds relative to rice, 
      enabling weeds to gain an advantage in interspecies competition, which is consistent with the figure. 
      Moreover, the overall evolutionary trend of the system remains approximately the same when \( \beta_{c\rightarrow w} \) varies within a certain range, 
      demonstrating system stability.
      \item Effect of \( \mathscr{K}_{crp} \) (maximum carrying capacity for rice):** As shown in Figure \ref{fig:Change_all} (C), 
      an increase in \( \mathscr{K}_{crp} \) results in an upward trend in rice biomass at any given time, and vice versa. 
      Ecologically, an increase in \( \mathscr{K}_{crp} \) indicates a higher potential maximum biomass for rice, 
      with rice biomass gradually approaching this value under suitable growth conditions, consistent with the figure. 
      Similarly, the overall evolutionary trend remains stable within a certain range of \( \mathscr{K}_{crp} \), further reflecting system stability.
      \item Effect of \( \sigma \) (standard deviation of Gaussian white noise):** As shown in Figure \ref{fig:Change_all} (D), 
      when \( \sigma \) is within a certain range, the trend of rice biomass over time remains approximately the same, 
      further demonstrating that the system's overall evolutionary trend is essentially unaffected. 
      Since \( \sigma \) is positively correlated with the amplitude of random fluctuations in the system, 
      this reflects the system's stability. However, it is noted that when \( \sigma = 0.1 \), rice goes extinct around week 70. 
      This occurs because large random fluctuations cause severe negative disturbances in the dynamics of rice biomass, 
      leading to its rapid decline to zero when the growth rate of \( W_{crp} \) is relatively low. 
      This illustrates that the system's stability and resilience to disturbances are finite, 
      which is consistent with the ecological concept of limited resistance and recovery in ecosystems.
    \end{itemize}
  \section{Evaluation of the Model}
    \subsection{Strengths}
    \subsection{Weaknesses}
  \section{Suggestions}

>>>>

      \includegraphics[width=\linewidth]{images/FlowCharts.pdf}
      \caption{Flow Charts of Our Work}
      \label{fig:FlowCharts}

@@

        It can be mathematically proven that, after incorporating these variations, 
        the LV-LG model system theoretically possesses non-trivial stable points when the parameters are within a certain range. 
        When the system is near these points, the ecosystem can recover from small perturbations, 
        reaching a dynamic ecological equilibrium.
      \subsection{Polination}
      \subsubsection{Soil Fertility}
        Now, we introduce the effect of soil fertility on plant growth.
        $i$ in the following statements represents rice or weed, $j$ the other.
        For the sake of simplicity in the model, 
        the influence of soil fertility on plant growth is divided into two main factors: 
        the effect of carbon dioxide (CO$_2$) concentration and the concentration of inorganic salts absorbed by the plants.

@@

    Below, we analyze the curves for each of the four scenarios:
    \begin{itemize}
      \item Effect of \( r_{crp} \) (natural growth rate of rice biomass): 
      As shown in Figure \ref{fig:Change_all} (A), an increase in \( r_{crp} \) leads to an upward trend in rice biomass at any given time, and vice versa. 
      From an ecological perspective, an increase in \( r_{crp} \) indicates a higher marginal growth rate of rice biomass, resulting in faster growth, 
      which aligns with the figure. On the other hand, 
      the overall evolutionary trend of the system remains approximately the same when \( r_{crp} \) varies within a certain range, 
      reflecting the system's stability.
      \item Effect of \( \beta_{c\rightarrow w} \) (weed-to-rice competition coefficient): As shown in Figure \ref{fig:Change_all} (B), 
      an increase in \( \beta_{c\rightarrow w} \) results in a downward trend in rice biomass and an upward trend in weed biomass at any given time, 
      and vice versa. Ecologically, an increase in \( \beta_{c\rightarrow w} \) reflects a higher competitive ability of weeds relative to rice, 
      enabling weeds to gain an advantage in interspecies competition, which is consistent with the figure. 
      Moreover, the overall evolutionary trend of the system remains approximately the same when \( \beta_{c\rightarrow w} \) varies within a certain range, 
      demonstrating system stability.
      \item Effect of \( \mathscr{K}_{crp} \) (maximum carrying capacity for rice): As shown in Figure \ref{fig:Change_all} (C), 
      an increase in \( \mathscr{K}_{crp} \) results in an upward trend in rice biomass at any given time, and vice versa. 
      Ecologically, an increase in \( \mathscr{K}_{crp} \) indicates a higher potential maximum biomass for rice, 
      with rice biomass gradually approaching this value under suitable growth conditions, consistent with the figure. 
      Similarly, the overall evolutionary trend remains stable within a certain range of \( \mathscr{K}_{crp} \), further reflecting system stability.
      \item Effect of \( \sigma \) (standard deviation of Gaussian white noise): As shown in Figure \ref{fig:Change_all} (D), 
      when \( \sigma \) is within a certain range, the trend of rice biomass over time remains approximately the same, 
      further demonstrating that the system's overall evolutionary trend is essentially unaffected. 
      Since \( \sigma \) is positively correlated with the amplitude of random fluctuations in the system, 
      this reflects the system's stability. However, it is noted that when \( \sigma = 0.1 \), rice goes extinct around week 70. 
      This occurs because large random fluctuations cause severe negative disturbances in the dynamics of rice biomass, 
      leading to its rapid decline to zero when the growth rate of \( W_{crp} \) is relatively low. 
      This illustrates that the system's stability and resilience to disturbances are finite, 
      which is consistent with the ecological concept of limited resistance and recovery in ecosystems.
    \end{itemize}
  \section{Evaluation of the Model}
    \subsection{Strengths}
    \subsection{Weaknesses}
  \section{Suggestions}
